Asymmetric functional prediction bands for assessing the validity of spatiotemporally smooth biomechanical curve data

### 2021-08-11 paper.Rmd
Adapt coverage functions

---
title: "Asymmetric functional prediction bands for assessing the validity of spatiotemporally smooth biomechanical curve data"
author:
  - name: Daniel Koska
    email: daniel.koska@hsw.tu-chemnitz.de
    affiliation: Chemnitz University of Technology, Research Methodology and Data Analysis in Biomechanics
    footnote: Corresponding Author
  - name: Doris Oriwol
    email: doris.oriwol@partner.kit.edu
    affiliation: Karlsruhe Institute of Technology
  - name: Christian Maiwald
    email: christian.maiwald@hsw.tu-chemnitz.de
    affiliation: Chemnitz University of Technology, Research Methodology and Data Analysis in Biomechanics
# address:
#   - code: Chemnitz University of Technology
#     address:  Thüringer Weg 11, 09126 Chemnitz
#   - code: Another University
#     address: Department, Street, City, State, Zip
abstract: |
  This is the abstract.

@@

# setwd(dir.script)
source(paste0(dir.script, "/example_data.R"))
source(paste0(dir.script, "/pick_subwise_curves.R"))
source(paste0(dir.script, "/draw_clusters.R"))
source(paste0(dir.script, "/floa_rcb.R"))
source(paste0(dir.script, "/floa_point.R"))
source(paste0(dir.script, "/floa_roislien.R"))
source(paste0(dir.script, "/plot_loa.R"))
source(paste0(dir.script, "/get_coverage.R"))
source(paste0(dir.script, "/crossval_coverage.R"))
source(paste0(dir.script, "/plot_cov_ver.R"))
```

@@

Leave-one (subject) out method to estimate the achieved coverage

Versions:

* v1   : n = length(subjects) random strides from all strides

* v2   : One random stride per subject

* v3   : Fetch a SINGLE random stride from all strides

* v4 : Roislien approach (Get one random stride from each subject ONCE and boot-
       strap the resulting sample (of length (n=length(subjects))

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "smooth", dir.data)
n.boot <- 100
floa <- floa_rcb(data, n.boot, ver = "v2")
plot_loa(data, floa, central.tendency = "mean")

@@

@@

n.boot <- 100
cover.cross <- crossval_coverage(data, n.boot)

plot_cov_ver(cover.cross)
```

<!-- #### v1 (n = length(subjects) random strides from all strides) -->

<!-- ```{r echo = FALSE, warning = FALSE, message = FALSE} -->
<!-- data <- example_data(dat = "smooth", dir.data) -->
<!-- ``` -->

<!-- ```{r echo = FALSE, warning = FALSE, message = FALSE} -->
<!-- floa <- floa_rcb(data, n.boot, ver = "v1") -->
<!-- floa.point <- floa_point(data) -->

<!-- cover.cross.v1 <- crossval_coverage(data, floa, floa.point, method = "all") -->

<!-- plot_cov_ver(cover.cross.v1) -->
<!-- ``` -->

<!-- #### V2 (One random stride per subject) -->

<!-- ```{r echo = FALSE, warning = FALSE, message = FALSE} -->
<!-- floa <- floa_rcb(data, n.boot, ver = "v2") -->
<!-- floa.point <- floa_point(data) -->

<!-- cover.cross.v2 <- crossval_coverage(data, floa, floa.point, method = "all") -->

<!-- plot_cov_ver(cover.cross.v2) -->
<!-- ``` -->

<!-- #### v3 (Fetch a SINGLE random stride from all strides) -->

<!-- ```{r echo = FALSE, warning = FALSE, message = FALSE} -->
<!-- floa <- floa_rcb(data, n.boot, ver = "v3") -->
<!-- floa.point <- floa_point(data) -->

<!-- cover.cross.v3 <- crossval_coverage(data, floa, floa.point, method = "all") -->

<!-- plot_cov_ver(cover.cross.v3) -->
<!-- ``` -->

@@

>>>>

---
title: "Asymmetric functional prediction bands for assessing the validity of spatiotemporally smooth biomechanical curve data"
author:
  - name: Daniel Koska
    email: daniel.koska@hsw.tu-chemnitz.de
    affiliation: Chemnitz University of Technology, Research Methodology and Data Analysis in Biomechanics
    footnote: Corresponding Author
  - name: Doris Oriwol
    email: doris.oriwol@partner.kit.edu
    affiliation: Karlsruhe Institute of Technology
  - name: Christian Maiwald
    email: christian.maiwald@hsw.tu-chemnitz.de
    affiliation: Chemnitz University of Technology, Research Methodology and Data Analysis in Biomechanics
# address:
#   - code: Chemnitz University of Technology
#     address:  Thüringer Weg 11, 09126 Chemnitz
#   - code: Another University
#     address: Department, Street, City, State, Zip
abstract: |
  Paper als short communication / technical note?

@@

source(paste0(dir.script, "/example_data.R"))
source(paste0(dir.script, "/pick_subwise_curves.R"))
source(paste0(dir.script, "/draw_clusters.R"))
source(paste0(dir.script, "/functional_mean.R"))
source(paste0(dir.script, "/functional_sd.R"))
source(paste0(dir.script, "/boot_mean_sd.R"))
source(paste0(dir.script, "/floa_rcb.R"))
source(paste0(dir.script, "/floa_point.R"))
source(paste0(dir.script, "/floa_roislien.R"))
source(paste0(dir.script, "/plot_loa.R"))
source(paste0(dir.script, "/get_coverage.R"))
source(paste0(dir.script, "/get_coverage_fraction.R"))
source(paste0(dir.script, "/crossval_coverage.R"))
source(paste0(dir.script, "/crossval_coverage_fraction.R"))
source(paste0(dir.script, "/plot_cov_ver.R"))
```

@@

Leave-one out method to estimate the achieved coverage

Prediction intervals are calculated from size.dataset = number.subjects - 1 and then validated against the left out subjects curves for five different methods:

* FLoA~RCB_v1~   : n = length(subjects) random strides from all strides

* FLoA~RCB_v2~   : One random stride per subject

* FLoA~RCB_v3~   : Fetch a SINGLE random stride from all strides

* FLoA~RCB_Roislien~ : Roislien approach (Get one random stride from each subject ONCE and boot-
       strap the resulting sample (of length (n=length(subjects))

* FLoA~RCB_Point~ : Pointwise B & A Limits of Agreement

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
data <- example_data(dat = "smooth", dir.data)
n.boot <- 400
floa <- floa_rcb(data, n.boot, ver = "v2")
plot_loa(data, floa, central.tendency = "mean")

@@

Displayed are boxes for five different methods:

* 1. FLoA~RCB_v1~ : n = length(subjects) random strides from all strides

* 2. FLoA~RCB_v2~ : One random stride per subject

* 3. FLoA~RCB_v3~ : Fetch a SINGLE random stride from all strides

* 4. FLoA~RCB_Roislien~ : Roislien approach (Get one random stride from each subject ONCE and boot-
       strap the resulting sample (of length (n=length(subjects))

* 5. FLoA~RCB_Point~ : Pointwise B & A Limits of Agreement

Coverages are displayed for two different scenarios:

* 1: Coverage of the entire curve

* 2: Percentage of curve points within the respective FLoA

#### Smooth, wave data (normal error, constant variance, no trend)

Coverage of the entire curve

@@

cover.cross <- crossval_coverage(data, n.boot)
# colnames(cover.cross) <- c("RCB_1", "RCB_2", "RCB_3", "Roislien_4", "Point_5")

plot_cov_ver(cover.cross)

# knitr::kable(cover.cross, caption = "Percentages (entire curve covered) for every leave one out fold")
```

Percentage of curve points within the respective FLoA

```{r echo = FALSE, warning = FALSE, message = FALSE}
# Display cross validation coverages (fraction of the curve that is covered) across methods
cover.cross.fraction <- crossval_coverage_fraction(data, n.boot)

plot_cov_ver(cover.cross.fraction)
```

#### Smooth wave data with nonlinear trend (constant variance)

Coverage of the entire curve

cover.cross <- crossval_coverage(data, n.boot)
# colnames(cover.cross) <- c("RCB_1", "RCB_2", "RCB_3", "Roislien_4", "Point_5")

plot_cov_ver(cover.cross)

# knitr::kable(cover.cross, caption = "Percentages (entire curve covered) for every leave one out fold")
```

Percentage of curve points within the respective FLoA

```{r echo = FALSE, warning = FALSE, message = FALSE}
# Display cross validation coverages (fraction of the curve that is covered) across methods
cover.cross.fraction <- crossval_coverage_fraction(data, n.boot)

plot_cov_ver(cover.cross.fraction)
```

#### Data with non-gaussian (Weibull distributed) error (no trend)

Coverage of the entire curve

cover.cross <- crossval_coverage(data, n.boot)
# colnames(cover.cross) <- c("RCB_1", "RCB_2", "RCB_3", "Roislien_4", "Point_5")

plot_cov_ver(cover.cross)

# knitr::kable(cover.cross, caption = "Percentages (entire curve covered) for every leave one out fold")
```

Percentage of curve points within the respective FLoA

```{r echo = FALSE, warning = FALSE, message = FALSE}
# Display cross validation coverages (fraction of the curve that is covered) across methods
cover.cross.fraction <- crossval_coverage_fraction(data, n.boot)

plot_cov_ver(cover.cross.fraction)
```

@@

It might be beneficial to work with functional data as suggested by Lenhoff et al. (1999) or Roislien et al. (2012) when e. g. interpolating data to a standardized length. This approach, however, wasn't necessary in this paper, since the synthetic data were created from functions and were designed to all have equal length (101 data points).
